---
title: "team"
output: html_document
---
git pull

git add files 
git commit -m "message"
git push
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco);
```

1.) What is the overall number of chocolate bars rated?

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
nrow(choco) #sums all of the rows in choco data set. 
```
## There are 1852 chocolate bars rated.

2.) How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
<<<<<<< HEAD

=======

```{r}
library(ggplot2)
ggplot(choco, aes(x=Review.Date, y=Rating)) + geom_bar(stat="identity") + 
  labs(x="Review Date", y="Rating")
```
## The number of ratings increases almost in linear fashion until the year 2015 and then drops rapidly into the middle of 2017



## Still need to finish NUMBER 3
3.) Which are the three locations with the most ratings? How do ratings compare across these company locations?
The locations with the most ratings are USA(787), France(158), and Canada(132).

```{r}
library(plyr)
# sum of the frequency of each location
freq <- count(choco, "Company.Location") 
print(freq)
# Canada = 132, France = 158, USA = 787

# sum the rows that have the value of Canada in the Company.Location column.
canada = subset(choco, Company.Location == "Canada")
# average the values of the ratings from the corresponding country. 
average_rating_canada = mean(canada$Rating, na.rm=TRUE)
france = subset(choco, Company.Location == "France")
average_rating_france = mean(france$Rating, na.rm=TRUE)
usa = subset(choco, Company.Location == "U.S.A.")
average_rating_USA = mean(usa$Rating, na.rm=TRUE)

print(average_rating_canada) # AVG. Canada Rating
print(average_rating_france) # AVG. France Rating
print(average_rating_USA) # AVG. USA Rating
```
#From when we look at the averages of the three countries with the largest number of ratings, we see that France has the largest average rating amongst all of their chocolates, then USA, and last Canada. 
4.) Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

What is the average rating amongst all rated chocolate bars? How does this compare to the Average of the countries with the top 3 most ratings from above? What does this mean?

5.) Answer the question from the dataset.

```{r}
average_rating = mean(choco$Rating, na.rm=TRUE)
# gets the average of the ratings column. If value equals null, then it is removed from the calculation. 
print(average_rating)
```
# The average of all the chocolate bar ratings is 3.19. This is below the average rating of French chocolate. This means that On average, the French chocolate is rated above average when using all the ratings as a a whole population. 

6.) Write one paragraph commenting on the workflow.

The workflow of this project consisted of communication between the two users that are using the cloned common repository. In our case, Jaydon worked on a certain set of questions and then pushed them to the repository. Then I pulled his changes and then finished the unfinished problems on my computer. When I finished the assignment I pushed it back onto the cloned repository and Jaydon pulled the finished assignment to check the overall work. 
