---
title: "team"
output: html_document
---
git pull

git add files 
git commit -m "message"
git push
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
head(choco);
```

1.) What is the overall number of chocolate bars rated?

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
nrow(choco)
```
## There are 1852 chocolate bars rated.

2.) How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
<<<<<<< HEAD

=======
>>>>>>> 131ecf2e869c6e4938df86cf1fb2f27eec820fa4
```{r}
library(ggplot2)
ggplot(choco, aes(x=Review.Date, y=Rating)) + geom_bar(stat="identity") + 
  labs(x="Review Date", y="Rating")
```
## The number of ratings increases almost in linear fashion until the year 2015 and then drops rapidly into the middle of 2017



## Still need to finish NUMBER 3
3.) Which are the three locations with the most ratings? How do ratings compare across these company locations?
The locations with the most ratings are USA(787), France(158), and Canada(132).

```{r}
library(plyr)
freq <- count(choco, "Company.Location")
print(freq)
# Canada = 132, France = 158, USA = 787

```

4.) Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

What is the average rating amongst all rated chocolate bars?

5.) Answer the question from the dataset.

```{r}
average_rating = mean(choco$Rating, na.rm=TRUE)
# gets the average of the ratings column. If value equals null, then it is removed from the calculation. 
print(average_rating)
```

6.) Write one paragraph commenting on the workflow.

The workflow of this project consisted of communication between the two users that are using the cloned common repository. In our case, Jaydon worked on a certain set of questions and then pushed them to the repository. Then I pulled his changes and then finished the unfinished problems on my computer. When I finished the assignment I pushed it back onto the cloned repository and Jaydon pulled the finished assignment to check the overall work. 
