---
title: "team"
output: html_document
---
git pull

git add files 
git commit -m "message"
git push
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.) What is the overall number of chocolate bars rated?

```{r}
choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
nrow(choco)
```
## There are 1852 chocolate bars rated.

2.) How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
library(ggplot2)
ggplot(choco, aes(x=Review.Date, y=Rating)) + geom_bar(stat="identity") + 
  labs(x="Review Date", y="Rating")
```
## The number of ratings increases almost in linear fashion until the year 2015 and then drops rapidly into the middle of 2017

3.) Which are the three locations with the most ratings? How do ratings compare across these company locations?

4.) Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

5.) Answer the question from the dataset.

6.) Write one paragraph commenting on the workflow.